\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-20 doc/incertae_sedis.tex
context about naming

@@

\paragraph{Information content of the \emph{incertae sedis }annotation}

>>>>

The interpretation of the \emph{incertae sedis} annotation affects the supertree
    pipeline at three points:
\begin{enumerate}
    \item The subproblem decomposition step relies on identifying uncontested nodes.
    Thus, varying interpretations of whether or not an \emph{incertae sedis}
    taxon can be placed within another taxon without contesting that taxon
    will affect the subproblem decomposition.
    \item When solving each subproblem, how taxon is represented as a rooted
    split can affect the solution found.
    As described below, the \emph{incertae sedis} annotation affects the 
        exclude groups of rooted split encodings.
    \item The step of assigning names to the supertree is affected by the 
        operational phylogenetic definition of each name.
\end{enumerate}

@@

In terms of phylogenetic nomenclature the supertree pipeline acts as
    the taxonomy defines a branch-based name \citep[see][]{deQueiroz2013}
    for each higher taxon of the form.
So for name labeling node $n$ in the taxonomic tree, 
    the operational definition would be:
    ``the clade defined by all taxa
    that are more closely related to $\mathcal{I}(n)$ than to
    $\mathcal{E}(n)$, if such a clade exists on the tree.''

\paragraph{Information content of the \emph{incertae sedis} annotation}
